%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
\usepackage{charter}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\bfseries\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{1pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\LARGE Parth Krishna} \\ \vspace{1pt}
     {Business Analyst} \\
    +91 7406338696 $\cdot$ \href{mailto:parthkrishna1998@gmail.com}{parthkrishna1998@gmail.com} $\cdot$ 
    \href{https://www.linkedin.com/in/parthkrishna/}{linkedin.com/in/parthkrishna/} $\cdot$
    Gurugram, India
\end{center}

% \setlength{\baselineskip}{10pt}

%-----------SUMMARY-----------
\section*{Professional Summary}
{}Passionate Business Analyst with experience integrating data-driven insights using analytical expertise and delivering high-impact end-to-end automation solutions, from process automation to the development of intuitive dashboards and web applications.
\newline
\\
Leveraging my programming expertise in Python and Microsoft PowerApps Suite, I excel in data extraction and manipulation, enabling data-driven decision-making and predictive analytics to perform Digital Transformation for global clients with a proven track record of collaborating with cross-functional teams including Operations, Finance, Healthcare and Environmental Safety \& Governance industry.

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\small{
    {Python SQL $\cdot$ Microsoft PowerApps \& Power Automate $\cdot$ Linux $\cdot$ Git $\cdot$  Tableau $\cdot$ CI/CD $\cdot$ Smartsheet $\cdot$ ServiceNow $\cdot$ Postman $\cdot$ Robotic Process Automation $\cdot$ Natural Language Processing $\cdot$ Quality Assurance $\cdot$ Business Process Mapping $\cdot$ KPI Reporting $\cdot$ Predictive Data Modelling $\cdot$ Generative AI $\cdot$ Cross-functional teamwork
    }}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Business Analyst}{Dec 2022 -- Present}
      {Genpact}{Gurugram}
      \resumeItemListStart
        \resumeItem{Worked with NAM \& LATAM clients to drive Ops Analytics goals by doing Process Automation to retain Data Integrity, resolve human error, improve efficiency and reduce operation time using tools like Tableau, Python \& MS Excel.}
        \resumeItem{Implemented a solution architecture with MS PowerApps Suite to aggregate data and seamlessly integrate triggered workflows along with AI Builder Sentiment Analysis to increase overall BI impact of more than \$40,000.}
        \resumeItem{Developed a versatile Python-based automation across different verticals using Lean Six Sigma Ideology which facilitated timely datasource refresh \& failure intimation. This aided the global region heads in the identification of impacted dashboards and addressing aging issues promptly.}
        \resumeItem{Deploying Predictive Analytics \& NLP based Machine Learning models to forecast resource utilization, future trends \& mitigate the risk in decision
        making to deliver requirements. Developed Python web application with interactive dashboards which helped in increased winning prospect.}
    \resumeItemListEnd

    \resumeSubheading
      {Senior Associate}{Feb 2021 - Nov 2022}
      {Genpact}{Gurugram}
      \resumeItemListStart
        \resumeItem{Handled EMEA region and delivered Operations goals by providing inventory \& order management. Engineered ServiceNow Workflows to create KPIs \& forecasting models by
        analyzing inventory data with Python to increase On-Time Delivery.}
        \resumeItem{Worked with AMER region to design a Data Quality-focused Python based packaged solution tailored to client needs, enhancing the evaluation of periodic reports. Resulted in a
        highly efficient planning process and improved overall productivity.}
      \resumeItemListEnd

      \resumeSubheading
      {Software Developer}{Jun 2019 - Aug 2020}
      {Invide Labs}{Remote}
      \resumeItemListStart
        \resumeItem{Established and managed AWS architecture, transitioning Django APIs into EC2 servers with elastic IP using automated pipelines Github Actions
        CI/CD and bash scripts.}
        \resumeItem{Developed and hosted custom Twitter bots which provided real-time traffic monitoring and analysis with NLP based word cloud generation.}
      \resumeItemListEnd

      \resumeSubheading
      {Subject Matter Expert - Cryptography \& Python}{Aug 2018 - May 2019}
      {PESU I\/O}{Bengaluru}
      \resumeItemListStart
        \resumeItem{Guided 100+ undergraduate students to intermediate expertise in cryptography and demonstrated various encryption and decryption techniques using bash and Python scripts.}
        \resumeItem{Mentored 50+ undergraduate students to intermediate proficiency in Python, illustrating essential concepts through code implementation for better comprehension.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%    \resumeSubHeadingListStart
%      \resumeProjectHeading
%          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%          \resumeItemListStart
%            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%            \resumeItem{Visualized GitHub data to show collaboration}
%            \resumeItem{Used Celery and Redis for asynchronous tasks}
%          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%          \resumeItemListEnd
%    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PES University}{Bengaluru}
      {B.Tech in Computer Science, Specialisation in Systems Design and Algorithms}{2016 - 2020}
  \resumeSubHeadingListEnd


%-----------Certifications-----------
\section{Certifications}
  \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Dataiku Core Designer} 
    }
    \item{
     \textbf{Dataiku ML Practitioner}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
